### 2018-12-05 tex/paper.tex
Experiments section for higher-order Potts model completed.

%\begin{figure}
%       \Tree [.root [.{m0} 0-3 ] [.{m1} 4-7 ] [.{m2} 8-11 ] [.{m3} 12-15 ] [.{m4} 16-19 ]]
%   %    \Tree [.root [.{m0} 0 1 2 3 ] [.{m1} 4 5 6 7 ] [.{m2} 8 9 10 11 ] [.{m3} 12 13 14 15 ] [.{m4} 16 17 18 19 ]]
%%    \Tree[. [. [.1 .2 .3]]]
%\mycaption{\footnotesize \em An $r$-HST defining pairwise distance among 20 labels used for upper-bound comparison with TRW. $m0$ stands for meta-label 0, and so on.}
%\label{fig:syn_rhst}
%\end{figure}
\begin{figure}
\centering
\includegraphics[scale = 0.50]{./figures/synthetic_upper_bound_comparison.pdf}
\mycaption{\footnotesize \em Upper-bound comparison using synthetic data. The
plot shows the ratio (Submod bound - TRW bound)/|TRW bound| averaged over 100
unary instances as a function of pairwise weights using the worst-case optimal and
alternate extension for Potts and hierarchical Potts models. We observe that
the worst-case optimal extension
(solid) results in tighter bounds as compared to the respective alternate
extensions (dotted). Also, the worst-case optimal extension bounds are in
similar range as the TRW bounds.}
\label{fig:syn_plot}
\end{figure}
\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.14]{\imagePath/stereo/venus_GT} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_mf} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_submod} &
    %
        \includegraphics[scale = 0.19]{\imagePath/stereo/tsukuba_GT} &
        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_mf} &
        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_submod} \\
        \scriptsize(a) Venus GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Tsukuba GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize  60.32s, 1.83e+07 &  \scriptsize 469.75s, {\bf 1.55e+07} & {} & \scriptsize  14.93s, 8.21e+06 & \scriptsize 215.22s, {\bf 4.12e+06} \\
         \includegraphics[scale = 0.14]{\imagePath/stereo/cones_GT} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_mf} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_submod} &
        %
       %
         \includegraphics[scale = 0.15]{\imagePath/stereo/teddy_GT} &
        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_mf} &
        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_submod} \\
    \scriptsize(a) Cones GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Teddy GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize 239.14s, 2.68e+07 &  \scriptsize 1082.72s, {\bf 1.27e+07} & {} & \scriptsize 555.30s, 2.36e+07 & \scriptsize 1257.86s, {\bf 1.58e+07}\\
\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with Potts
compatibility and Gaussian pairwise potentials. We compare our solution with
the mean-field algorithm of Koltun and Krahenbuhl \citep{koltun2011efficient}. We observe that our method gives better-looking solutions with lower energy value at the cost of higher computational time.}
\label{fig:stereo}
\end{figure*}

@@

\mysubsection{Stereo Matching using Higher-order Potts Model}
\label{subsec:stereo_hop}
\myparagraph{Data} Next, we use the higher-order Potts model for stereo
matching on the Middlebury dataset. For this
purpose, we take a dense CRF model with Potts compatibility term and Gaussian pairwise
potentials, and augment it with higher-order Potts term.

@@

\myparagraph{Results} Figure \ref{fig:stereo_hop} shows some example solutions obtained by picking the
label with maximum marginal probability for each variable.

>>>>

%\begin{figure}
%       \Tree [.root [.{m0} 0-3 ] [.{m1} 4-7 ] [.{m2} 8-11 ] [.{m3} 12-15 ] [.{m4} 16-19 ]]
%   %    \Tree [.root [.{m0} 0 1 2 3 ] [.{m1} 4 5 6 7 ] [.{m2} 8 9 10 11 ] [.{m3} 12 13 14 15 ] [.{m4} 16 17 18 19 ]]
%%    \Tree[. [. [.1 .2 .3]]]
%\mycaption{\footnotesize \em An $r$-HST defining pairwise distance among 20 labels used for upper-bound comparison with TRW. $m0$ stands for meta-label 0, and so on.}
%\label{fig:syn_rhst}
%\end{figure}
\begin{figure}
\centering
\includegraphics[scale = 0.50]{./figures/synthetic_upper_bound_comparison.pdf}
\mycaption{\footnotesize \em Upper-bound comparison using synthetic data. The
plot shows the ratio (Submod bound - TRW bound)/|TRW bound| averaged over 100
unary instances as a function of pairwise weights using the worst-case optimal and
alternate extension for Potts and hierarchical Potts models. We observe that
the worst-case optimal extension
(solid) results in tighter bounds as compared to the respective alternate
extensions (dotted). Also, the worst-case optimal extension bounds are in
similar range as the TRW bounds.}
\label{fig:syn_plot}
\end{figure}

\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.14]{\imagePath/stereo/venus_GT} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_mf} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/venus_left_submod} &
    %
        \includegraphics[scale = 0.19]{\imagePath/stereo/tsukuba_GT} &
        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_mf} &
        \includegraphics[scale = 0.19]{\imagePath/stereo/potts/tsukuba_left_submod} \\
        \scriptsize(a) Venus GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Tsukuba GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize  60.32s, 1.83e+07 &  \scriptsize 469.75s, {\bf 1.55e+07} & {} & \scriptsize  14.93s, 8.21e+06 & \scriptsize 215.22s, {\bf 4.12e+06} \\
         \includegraphics[scale = 0.14]{\imagePath/stereo/cones_GT} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_mf} &
        \includegraphics[scale = 0.14]{\imagePath/stereo/potts/cones_left_submod} &
        %
       %
         \includegraphics[scale = 0.15]{\imagePath/stereo/teddy_GT} &
        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_mf} &
        \includegraphics[scale = 0.15]{\imagePath/stereo/potts/teddy_left_submod} \\
    \scriptsize(a) Cones GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution & \scriptsize(a) Teddy GT & \scriptsize(b) MF solution & \scriptsize(c) Submod solution\\
        {} & \scriptsize 239.14s, 2.68e+07 &  \scriptsize 1082.72s, {\bf 1.27e+07} & {} & \scriptsize 555.30s, 2.36e+07 & \scriptsize 1257.86s, {\bf 1.58e+07}\\
\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with Potts
compatibility and Gaussian pairwise potentials. We compare our solution with
the mean-field algorithm of Koltun and Krahenbuhl \citep{koltun2011efficient}. We observe that our method gives better-looking solutions with lower energy value at the cost of higher computational time.}
\label{fig:stereo}
\end{figure*}

@@

\begin{figure*}
    \centering
\begin{tabular}{cccccc}
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_GT} &
        \includegraphics[scale = 0.22]{\imagePath/stereo/higher_potts/tsukuba_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/baby1_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/baby1_hop} &
        \includegraphics[scale = 0.34]{\imagePath/stereo/higher_potts/flowerpots_GT} &
        \includegraphics[scale = 0.16]{\imagePath/stereo/higher_potts/flowerpots_hop} \\
        \scriptsize(a) Tsukuba GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Baby1 GT & \scriptsize(b) Submod solution
        & \scriptsize(a) Flowerpots GT & \scriptsize(b) Submod solution\\
\end{tabular}
%\vspace{2mm}
\mycaption{\footnotesize \em Stereo matching using dense CRFs with higher-order
  Potts term in addition to Potts compatibility and Gaussian pairwise potentials.}
\label{fig:stereo_hop}
\end{figure*}

\mysubsection{Stereo Matching using Higher-order Potts Model}
\label{subsec:stereo_hop}
\myparagraph{Data} Next, we use the higher-order Potts model for stereo matching on the Middlebury dataset. Higher-order Potts model is suitable to be used for only some images in the dataset, since others have gradually sloping surfaces and higher-order cliques will force all pixels on these surfaces to take similar disparity values.  We take a dense CRF model with Potts compatibility term and Gaussian pairwise potentials, and augment it with higher-order Potts term. We obtain higher-order cliques by using super-pixels obtained from mean-shift algorithm \citep{comaniciu2002mean}.

@@

\myparagraph{Results} Figure \ref{fig:stereo_hop} shows some example solutions obtained by picking the
label with maximum marginal probability for each variable. We observe that our method gives results that are reasonably close to the ground-truth.
